---
title: "Alcohol vs Seat choice"
author: "Sierra Lander"
date: "Summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

## Introduction 

$H_0$:  There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.   

$H_A$: The average number drinks is different between at least two rows.   


## Methods 

Average number of drinks (alcohol) is a numerical value    
Seat choice is a categorical Value    
 We used helper file Cat~Num    



## Our Goal is to answer this question Is there a difference between thealcohol consumed between the row  you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

## Inferential Tests

## Conclusions


